---
title: "Mutlti100_NMQ6A"
output: html_notebook
---

# Load packages

```{r}
library(haven)
library(performance)
library(ggeffects)
library(dplyr)
library(broom)
```

# Import data and scale predictors

```{r}
df <- read_sav("input/Zunick_GranadosSamayoa_Fazio_JESP2017_WorkingData.sav")
df$WBz <- scale(df$bf_wb)
df$bscsZ <- scale(df$bscsmean)
```

# Inspect distribution

Count data, appears to be 1 or 0 inflated

```{r}
hist(df$unsolvpass3m)
```

# Linear regression violates assumptions

DV is count data so linear regression violates assumptions.

```{r}
modelMain.l <- lm(unsolvpass3m ~ WBz,
              data=df)
check_model(modelMain.l)
```

# Poisson Generalized Linear Model

Count data. Test main effect of weighting bias on unsolvable passes. Nonsignificant effect.

```{r}
modelMain.p <- glm(unsolvpass3m ~ WBz,
              data=df,
              family="poisson")
summary(modelMain.p)
confint(modelMain.p)
```

## Check assumptions for Poisson regression

Poisson is underfitting 0s. There is overdispersion for Poisson as well.

```{r}
check_zeroinflation(modelMain.p)
check_overdispersion(modelMain.p)
check_model(modelMain.p)
```

# Negative Binomial

Negative binomial for count data given Poisson underfit 0s and had overdispersion.

Nonsignificant main effect.

```{r}
modelMain.nb <- glm.nb(unsolvpass3m ~ WBz,
              data=df)
summary(modelMain.nb)
confint(modelMain.nb)
```

## Odds Ratio

```{r}
tidy(modelMain.nb,conf.int=TRUE,exponentiate=TRUE)
```

## Check assumptions

No more overdispersion with negative binomial. There is now overfitting of 0s rather than underfitting but it's pretty nominal and less overfitting than the underfitting that was observed for Poisson.

```{r}
check_model(modelMain.nb)
check_overdispersion(modelMain.nb)
check_zeroinflation(modelMain.nb)
```
# Interaction between weighting bias and self-control

Weighting bias positively predicts unsolvable passes/giving up for those low in self-control (-1SD). Negative association for those high in self-control (+1SD).

```{r}
modelBSCS.nb <- glm.nb(unsolvpass3m ~ as.numeric(WBz)*as.numeric(bscsZ),
              data=df)
summary(modelBSCS.nb)
confint(modelBSCS.nb)
ggpredict(modelBSCS.nb, c("WBz","bscsZ")) %>% plot()
```

## Odds Ratio

```{r}
tidy(modelBSCS.nb,conf.int=TRUE,exponentiate=TRUE)
```


# Conclusion

The claim was supported.

